Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2022-02-01 paper.tex
Remove 'nonlinear' from growth rate estiamtes. Unlcear if linear or nonlinear

Despite the flute instability appearing in the isotropic case
(Figure~\ref{fig:field_line_plots_iso}), only in the anisotropic case can the
onset of both the flute and kink instabilities be seen in the kinetic energy
profile shown in Figure~\ref{fig:kink_ke_log-4}. Here, the nonlinear growth
rates of the two instabilities are found to be $\gamma = 0.69$ for the flute
and $\lambda = 2.55$ for the kink. The onset times are approximately $t=27$ for
the flute instability and $t=29.5$ for the kink. In the isotropic case, the
growth rate of the kink, $\lambda = 2.97$, is larger than in the anisotropic
case, although the onset times appear similar, and the kinetic energy profile
shows no evidence of flute instability growth.

@@

\begin{table*}
\caption{\rev{\sout{Quantitative differences in the observed perturbations between results
\rev{with} different resistivity values $\eta$. In all measurements the
anisotropic viscosity model is used except for $k_\text{kink}$ where the
isotropic viscosity model us used. Measurements times are listed in the main
text.} JAMIE, PLEASE CHECK VALUES IN RED [rs]} Quantitative differences in the observed perturbations between results
\rev{with} different \rev{viscosity models and} resistivity values
$\eta$. Measurements times are listed in the main text.} 
\centering
\begin{tabular}{ccccc}
&\multicolumn{2}{c}{\rev{$\eta=10^{-4}$}}& \multicolumn{2}{c}{\rev{$\eta=10^{-3}$}} \\
&
Anisotropic &
Isotropic &
Anisotropic &
Isotropic \\
\midrule
Theoretical average ideal linear growth rate of flute $\gamma$
& 0.88 
& \rev{0.88} 
& 1.73 
& \rev{1.73} \\
\rev{Theoretical average resistive linear growth rate of flute $\gamma_r$}
& 0.35 
& 0.33
& 1.26 
& 1.25 \\
Observed nonlinear growth rate of flute $\gamma$
& 0.69 
& \rev{--} 
& 1.06 
& \rev{1.06}\\
Observed growth rate of kink $\lambda$
& 2.55 
& \rev{2.97} 
& 0.15 
& \rev{0.15}\\
\midrule
Theoretical radius $r_s$ of peak ideal flute growth rate
& 0.125 
& \rev{0.125} 
& 0.163 
& \rev{1.63}\\
\rev{Theoretical radius $\tilde{r}_s$ of peak resistive flute growth rate}
& 0.125 
& 0.125 
& 0.148 
& 0.140\\
Observed radius $r_s$ of peak flute growth rate
& 0.125 
& \rev{--} 
& 0.163 
& \rev{??}\\
\midrule
Observed axial wave number $k_{\text{flute}}$
& 23.61 
& \rev{--} 
& 16.05 
& \rev{??} \\
Observed axial wave number $k_{\text{kink}}$
& \rev{??} 
& 4.57 
& \rev{??} 
& 4.53\\
\midrule
\rev{Cumulative viscous heat at $t=50$}
& $1.64 \times 10^{-2}$ 
& 1.28 
& $2.89 \times 10^{-3}$ 
& 0.370 \\
\rev{Cumulative Ohmic heat at $t=50$}
& 3.06 
& 2.75 
& 6.54 
& 6.27 \\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table*}

>>>>

Despite the flute instability appearing in the isotropic case
(Figure~\ref{fig:field_line_plots_iso}), only in the anisotropic case can the
onset of both the flute and kink instabilities be seen in the kinetic energy
profile shown in Figure~\ref{fig:kink_ke_log-4}. Here, the growth
rates of the two instabilities are found to be $\gamma = 0.69$ for the flute
and $\lambda = 2.55$ for the kink. The onset times are approximately $t=27$ for
the flute instability and $t=29.5$ for the kink. In the isotropic case, the
growth rate of the kink, $\lambda = 2.97$, is larger than in the anisotropic
case, although the onset times appear similar, and the kinetic energy profile
shows no evidence of flute instability growth.

@@

\begin{table*}
\caption{\rev{\sout{Quantitative differences in the observed perturbations between results
\rev{with} different resistivity values $\eta$. In all measurements the
anisotropic viscosity model is used except for $k_\text{kink}$ where the
isotropic viscosity model us used. Measurements times are listed in the main
text.} JAMIE, PLEASE CHECK VALUES IN RED [rs]} Quantitative differences in the observed perturbations between results
\rev{with} different \rev{viscosity models and} resistivity values
$\eta$. Measurements times are listed in the main text.} 
\centering
\begin{tabular}{ccccc}
&\multicolumn{2}{c}{\rev{$\eta=10^{-4}$}}& \multicolumn{2}{c}{\rev{$\eta=10^{-3}$}} \\
&
Anisotropic &
Isotropic &
Anisotropic &
Isotropic \\
\midrule
Theoretical average ideal linear growth rate of flute $\gamma$
& 0.88 
& \rev{0.88} 
& 1.73 
& \rev{1.73} \\
\rev{Theoretical average resistive linear growth rate of flute $\gamma_r$}
& 0.35 
& 0.33
& 1.26 
& 1.25 \\
Observed growth rate of flute $\gamma$
& 0.69 
& \rev{--} 
& 1.06 
& \rev{1.06}\\
Observed growth rate of kink $\lambda$
& 2.55 
& \rev{2.97} 
& 0.15 
& \rev{0.15}\\
\midrule
Theoretical radius $r_s$ of peak ideal flute growth rate
& 0.125 
& \rev{0.125} 
& 0.163 
& \rev{1.63}\\
\rev{Theoretical radius $\tilde{r}_s$ of peak resistive flute growth rate}
& 0.125 
& 0.125 
& 0.148 
& 0.140\\
Observed radius $r_s$ of peak flute growth rate
& 0.125 
& \rev{--} 
& 0.163 
& \rev{??}\\
\midrule
Observed axial wave number $k_{\text{flute}}$
& 23.61 
& \rev{--} 
& 16.05 
& \rev{??} \\
Observed axial wave number $k_{\text{kink}}$
& \rev{??} 
& 4.57 
& \rev{??} 
& 4.53\\
\midrule
\rev{Cumulative viscous heat at $t=50$}
& $1.64 \times 10^{-2}$ 
& 1.28 
& $2.89 \times 10^{-3}$ 
& 0.370 \\
\rev{Cumulative Ohmic heat at $t=50$}
& 3.06 
& 2.75 
& 6.54 
& 6.27 \\
\end{tabular}
\label{tab:kink_fluting_params}
\end{table*}
